A Comparison of Parallel Graph Processing Benchmarks

### 2017-02-17 papers/publication/paper-pollard.tex
Made it 12, not 13 pages

We found that GraphMat is only decently performant, but scales to more threads. One explanation is that GraphMat's underlying computation model (sparse matrix operations), paired with the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation, is better suited to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]

>>>>

%We found that GraphMat is only decently performant, but scales to more threads. One explanation is that GraphMat's underlying computation model (sparse matrix operations), paired with the increased overhead of GraphMat's doubly-compressed sparse row (DSCR) graph representation, is better suited to larger-scale graphs.
% Furthermore, sparse matrix operations have been well studied so achieving good scalability is more realistic [cite]
